---
title: "Homework 3 solutions"
author: "Yanhao Li"
date: "10/9/2020"
output: github_document
---

```{r set_up, include = FALSE}
library(tidyverse)
library(p8105.datasets)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)


scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

### Problem 1

```{r}
data("instacart")
```

Short description of the dataset:

This dataset contains `r nrow(instacart)` rows and `r ncol(instacart)` columns.

Observations are the level of items in orders by user. There are user / order variables -- user ID, order ID, order day and order hour. There are also item variables -- name, aisle, department, and some numeric codes.

How many aisles, and which are most items from?

```{r}
instacart %>% 
  count(aisle) %>% 
  arrange(desc(n))
```

Let's make a plot.

```{r}
instacart %>% 
  count(aisle) %>% 
  filter(n > 10000) %>% 
  mutate(
    aisle = factor(aisle),
    aisle = fct_reorder(aisle, n)
  ) %>% 
  ggplot(aes(x = aisle, y = n)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

Let's make a table.

```{r}
instacart %>% 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
  group_by(aisle) %>% 
  count(product_name) %>% 
  mutate(rank = min_rank(desc(n))) %>% 
  filter(rank < 4) %>% 
  arrange(aisle, rank) %>% 
  knitr::kable()
```

Apples vs ice cream ..

```{r}
instacart %>% 
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
  group_by(product_name, order_dow) %>% 
  summarize(mean_hour = mean(order_hour_of_day)) %>% 
  pivot_wider(
    names_from = order_dow,
    values_from = mean_hour
  )
```

### Problem 2

Load, tidy and otherwise wrangle the data.

```{r l_t_w}
accel_df =
  read_csv("./accel_data.csv") %>% 
  janitor::clean_names() %>% 
  pivot_longer(
    activity_1:activity_1440,
    names_to = "minute_of_the_day",
    names_prefix = "activity_",
    values_to = "activity_count"
  ) %>% 
  mutate(
    day = factor(
      day, 
      levels = c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday")
      ),
    minute_of_the_day = as.numeric(minute_of_the_day),
    weekday_vs_weekend = recode(
      day,
      Monday = "weekday",
      Tuesday = "weekday",
      Wednesday = "weekday",
      Thursday = "weekday",
      Friday = "weekday",
      Saturday = "weekend",
      Sunday = "weekend"
    ),
    weekday_vs_weekend = factor(weekday_vs_weekend)
  ) %>% 
  arrange(week, day) %>% 
  select(-day_id)
```

Describe the resulting dataset:

The resulting dataset contains variables including `r colnames(accel_df)`. I arrange the dataset according to "week" variable firstly, then by "day" variable. "minute_of_the_day" variable shows each minute at specific day of the specifc week. "activity_count" variable shows activity counts for each minute of a 24-hour day starting at midnight. "weekday_vs_weekend" variable shows type of this day.

In total, there are `r nrow(accel_df)` observations. 

Create a table showing total activity over the days.

```{r c_t_d}
accel_df %>% 
  group_by(week, day) %>% 
  summarize(activity_of_the_day = sum(activity_count)) %>% 
  pivot_wider(
    names_from = day,
    values_from = activity_of_the_day
  )
```

